Think again?\\ The amount of mental simulation tracks uncertainty in the outcome

### 2015-04-30 manuscript.tex
Minor clarifications, grant information

\begin{table}
    \centering
    \begin{tabular}{ccl}
    \toprule
    \textbf{Model} & \textbf{Bounces} & \textbf{Correlation} \\
    \midrule
    $T=1$ & 0   & \NoSamplesHoleRTCorrZeroBounces{} \\
          & 1   & \NoSamplesHoleRTCorrOneBounce{} \\
          & 2   & \NoSamplesHoleRTCorrTwoBounces{} \\
          & all & \NoSamplesHoleRTCorr{} \\
    \midrule
    $T=2$ & 0   & \HoleRTCorrZeroBounces{} \\
          & 1   & \HoleRTCorrOneBounce{} \\
          & 2   & \HoleRTCorrTwoBounces{} \\
          & all & \HoleRTCorr{} \\
    \bottomrule
    \end{tabular}
    \caption{Correlations between human and model RTs.}
    \label{tbl:rt}
\end{table}

@@

Mental simulation is a powerful and flexible tool, as it offers us a way to make predictions about scenarios that have not yet come to pass, or which may never come to pass.
In this work, we demonstrated that when people use mental simulation, they are sensitive to their own uncertainty in reasoning about the task and accordingly adjust how many simulations they run.
This results joins others \cite<e.g.>{Hamrick:2014wq} in explaining not just \emph{that} people use simulation to reason about the world, but \emph{how} they use it.
While there are still many questions left unanswered---e.g., how do people use simulations in non-binary tasks?---this work brings us one step closer to understanding of how mental simulation is used.

@@

This work was supported by \TODO{}

@@

We recruited \PaddleNumComplete{} participants using psiTurk \cite{McDonnell12}.
Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for 5 minutes of work.
We excluded \PaddleNumFailed{} participants for failing to catch the ball on more than one control trial.

>>>>

\begin{table}
    \centering
    \begin{tabular}{ccl}
    \toprule
    \textbf{Model} & \textbf{Bounces} & \textbf{Correlation} \\
    \midrule
    $T=1$ & 0   & \NoSamplesHoleRTCorrZeroBounces{} \\
          & 1   & \NoSamplesHoleRTCorrOneBounce{} \\
          & 2   & \NoSamplesHoleRTCorrTwoBounces{} \\
          & all & \NoSamplesHoleRTCorr{} \\
    \midrule
    $T=2$ & 0   & \HoleRTCorrZeroBounces{} \\
          & 1   & \HoleRTCorrOneBounce{} \\
          & 2   & \HoleRTCorrTwoBounces{} \\
          & all & \HoleRTCorr{} \\
    \bottomrule
    \end{tabular}
    \vspace{.25cm}
    \caption{\textbf{Correlations between human and model RTs.} The SPRT model ($T=2$) can capture variations in RTs within bounce conditions, while the single sample model ($T=1$) cannot. Note that the correlations for the $T=1$ model are non-zero because we estimate $\mathbb{E}[B]$ from the simulation model, so there is some variation in the expected number of bounces across stimuli.}
    \label{tbl:rt}
\end{table}

@@

Mental simulation is a powerful and flexible tool, as it offers a way to make predictions about scenarios that have not yet (or may never) come to pass.
In this work, we demonstrated that when people use mental simulation, they are sensitive to their own uncertainty in reasoning about the task and accordingly adjust how many simulations they run.
This results joins others \cite<e.g.>{Hamrick:2014wq} in explaining not just \emph{that} people use simulation to reason about the world, but \emph{how} they use it.
While there are still many questions left unanswered---e.g., how do people use simulations in non-binary tasks?---this work brings us one step closer to understanding of how mental simulation is used.

@@

This work was supported by a NSF GRF awarded to JBH, a UCSD Chancellor’s Interdisciplinary Collaboratories grant awarded to KAS, NSF CPS grant 1239323, and \TODO{}.

@@

We recruited \PaddleNumComplete{} participants using psiTurk \cite{McDonnell12}.
Participants were treated in accordance with UC Berkeley IRB standards and were paid \$0.60 for 5 minutes of work.
We excluded \PaddleNumFailed{} people for failing to catch the ball on more than one control trial.
